\textbf{Hardware accelerator topologies in heterogeneous systems: an evaluation in the security domain}

### 2019-12-09 reports/paper.tex
wording
synthesis results

\subsection{Full-scale SoC simulation}

@@

@@

\begin{itemize}
\item Pure software: ECB and CBC mode
\item MMIO accelerator, single: ECB and CBC mode
\item MMIO accelerator, automatic: ECB mode
\item Tightly-coupled accelerator: ECB and CBC mode
\item Hybrid accelerator: ECB mode
\end{itemize}

@@

% TODO small interpretation paragraph here
The hybrid accelerator is significantly faster than all other implementations
tested. This is to be expected since the accelerator itself performs the memory
requests without intervention of the CPU, directly into the memory bus. The
MMIO accelerator in the automatic mode comes in as second fastest. This
is also to be expected in comparison with the RoCC accelerator for example,
since the latter is run in interactive mode, that is, the application code
issues each round sequentially and sequential rounds are not immediately
executed by the CPU, due to buffering and communication logic in the RoCC
adapter fabric, in contrast to the former where rounds occur immediately (next
clock cycle) one after the other.

@@

@@

\begin{itemize}
  \item In some configurations, accelerators can only perform in ECB mode in
    hardware, limiting both security and performance. To overcome this, the
    accelerator implementation needs to be extended to be more flexible/complex
    and include such operation modes.
  \item Due to the use of generic instruction / RoCC interface, accelerators
    can be exploited by attacker at unprivileged level. To overcome this,
    accelerators and toolchain must be modified to use customized instructions,
    which can be configured for certain privilege levels only
\end{itemize}

>>>>

\subsection{Full SoC simulation}

@@

We generate a system that targets Digilent's Arty FPGA board, then use Xilinx
Vivado to perform synthesis and implementation and extract metrics.

@@

\begin{itemize}
\item Software only: ECB and CBC mode
\item MMIO accelerator, single: ECB and CBC mode
\item MMIO accelerator, automatic: ECB mode
\item Tightly-coupled accelerator: ECB and CBC mode
\item Hybrid accelerator: ECB mode
\end{itemize}

@@

% TODO small interpretation paragraph here
The hybrid accelerator is significantly faster than all other implementations
tested. This is to be expected since the accelerator itself performs the memory
requests without intervention of the CPU, directly into the memory bus. The
MMIO accelerator in the automatic mode comes in as second fastest. This
is also to be expected in comparison with the RoCC accelerator for example,
since the latter is run in interactive mode, that is, the application code
issues each round sequentially and sequential rounds are not immediately
executed by the CPU, due to buffering and communication logic in the RoCC
adapter fabric, in contrast to the former where rounds occur immediately (next
clock cycle) one after the other. The MMIO accelerator in single mode greatly
suffers from the need to access the memory bus for each operation, ultimately
making it slower than software.

@@

Synthesis and implementation are performed using Vivado. This is only done
once, for the MMIO accelerator, as the core implementation of Simon is shared
across all accelerators. Usage as reported by vivado is at 3119 LUTs and 2004
flip flops, which account for approximately 17\% and 19.5\% of the total design
(SoC) size.

The somewhat large size of the accelerator design stems mainly from the
unoptimized key expansion function, which accounts for roughly 75\% and 83.5\%
of the flip flop and LUT usage for the entire accelerator. The round function
accounts for the rest of the usage.

\subsection{Power}

Estimated power consumption is also reported after synthesis and implementation
using Vivado. It is reported as 8mW for the simon accelerator alone --- the
entire SoC power consumption is estimated at 252 mW (HWACC accounts for \approx 3\%).

As is the case for area, power the key expansion is also responsible for the
majority of power consumption, approximately 87.5\% of the total for the accelerator.

@@

\begin{itemize}
  \item In some configurations, accelerators can only perform in ECB mode in
    hardware, limiting both security and performance. To overcome this, the
    accelerator implementation needs to be extended to be more flexible/complex
    and include such operation modes.
  \item Due to the use of generic instruction / RoCC interface, accelerators
    can be exploited by attacker at unprivileged level. To overcome this,
    accelerators and toolchain must be modified to use customized instructions,
    which can be configured for certain privilege levels only.
\end{itemize}
